---
title: "STA426_Exercise1b"
author: "Rachel McLeod"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Visualising data from the log-normal distribution

This short document will take you through the stages of randomly sampling 100 values from the log-normal distribution where $\mu$ = 1 and $\sigma$ = 0.25, visualising these data as  a histogram on a normal and log scale before finally presenting some descriptive statistics of the data.

# Sampling values

```{r sampling}
data <- rlnorm(100, 1, 0.25)
```

# Plotting values

The generated values are then plotted as a histogram.

On a normal scale:

```{r histo, echo=TRUE}
h <- hist(data, breaks = 10)
```

On a log scale:

```{r logscale, echo=TRUE}
l <- hist(log(data), breaks = 10)
```
```{r stats, echo=FALSE}
mean <- mean(data)
stddev <- sd(data)
```

# Descriptive Statistics

The mean of the data is `r mean` and the standard deviation is `r stddev`.